Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-17 doc/GMP2015/s02_preliminaries.tex
Updated preliminary

%Define rigidity matroid and combinatorial characterization of independence/rigidity next
%Laman's theorem (for bar-joint rigidity matroid), 
%cite also Lovasz Yemini
%Cite other combinatorial characterizations for other types of constraint systems/hyper graphs:
%Tay and Whiteey, White and Whitelely,  
%Streinu Theran (k,l)-sparsity matroid

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % %

%A subset of edges $E'$, or a subgraph $(V', E')$, of a graph $G = (V, E)$ is said to be {\it independent} in $d$-dimensions, when the set of rows of $R_d(G)$ corresponding to $E'$ is generically independent, or independent for a generic instantiation of the indeterminate entries. 
%This yields the $d$-dimensional generic {\it rigidity matroid} associated with a graph $G$.

%The graph is  {\it infinitesimally rigid} if %the rigidity matrix has full rank, that is, 
%if the number of generically independent rows or the rank of $R_d(G)$ is maximal.
%In the case of linkage, the maximal rank is $d|V| - {d+1 \choose 2}$, where ${d+1 \choose 2}$ is the number of rotational and translational degrees-of-freedom of a rigid body in $\mathbb{R}^d$ [?].
%A vector in the kernel of the rigidity matrix is called an {\it infinitesimal motion vector}.

%A graph $G = (V,E)$ is:
%\begin{itemize}
%	\item generically {\it isostatic (minimally rigid, well-constrained)} if $R_d(G)$ has full rank
%	\item \textbf{rigid} if there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.
%	\item {\it flexible} if $G$ is not rigid
%    \item \textbf{under-constrained} if $G$ is independent and not rigid.
%    \item \textbf{over-constrained} if it is not independent.
%\end{itemize}
%In this paper all results are about independent - underconstrained or
%isostatic

@@

% A generalized version of Asimow Roth (implicit fn thm) states that
% generic rigidity, i.e.\ there exist at most finitely many solutions to the system at generic points,  %to the algebraic system 
%  is equivalent to  our definition  of infinitesimal rigidity based on indeterminates.

%\todo{--rigidity matroid\\
%--Combinatorial characterization of rigidity matroid
%Example: Laman's theorem for bar-joint (refer to others)
%Lovasz Yemini
%Tay white and whiteley
%(citations)
%+ pinned line incidence and multi-body-pin (in application
%section)}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

%Standard except for generality and ordering and the fact that I want to
%avoid the use of the word framework if possible. Do everything
%with constraint systems, linearization and genericity using indeterminates.

%--general  geometric constraint system --

%A $d$-dimensional {\it geometric constraint system} in general consists of
%
%- a underlying {\it constraint graph} $G=(V,E)$, or more generally, a hypergraph, whose  vertices represents geometric primitives in $d$-dimension and whose (hyper)edges specifies the combinatorics of constraints between pairs/tuples of the geometric primitives.
%- an {\it algebraic system of  constraint functions} from $E$ to the domain of constraint value
%In this paper we study qusecs, a class of 2D geometric constrain system that is independent (defined below).

%--underlying constraint graph or hypergraph (common treatment)

%--linearization: Jacobian of constraint system,
%rigidity matrix of indeterminates
%
%The algebraic system can usually be linearized at {\it generic} points
%by taking the Jacobian of the system,
%giving  the $d$-dimensional {\it rigidity matrix } $R_d(G)$ of a the (hyper)graph $G = (V,E)$, 
%whose rows correspond to edges, columns correspond to coordinate positions of vertices,  entries are \emph{indeterminates} representing the coordinate position $\mathbf{p}(v) \in \mathbb{R}^d$ of the geometric primitives corresponding to vertices $v \in V$.

%-- give example for the case of
%linkages
%
%In the case of linkage, 
%let $p_1(v), p_2(v), \ldots, p_d(v)$ represent the coordinate position $\mathbf{p}(v) \in \mathbb{R}^d$ of the joint corresponding to a vertex $v \in V$. 
%The matrix $R_d(G)$ has one row for each edge $e \in E$ and $d$ columns for each vertex $v \in V$.  The row corresponding to $e = \{u,v\} \in E$ represents the bar connecting $p(u)$ and $p(v)$ and has $d$ non-zero indeterminate entries $\mathbf{p}(u)-\mathbf{p}(v)$ (resp.\ $\mathbf{p}(v)-\mathbf{p}(u)$) in the $d$ columns corresponding to $u$ (resp.  $v$) and zero in the other entries.

%%Let $p_1(v), p_2(v), \ldots, p_d(v)$ represent the coordinate position $\mathbf{p}(v) \in \mathbb{R}^d$ of the joint corresponding to a vertex $v \in V$. 
%The matrix $R_d(G)$ has one row for each edge $e \in E$ and $d$ columns for each vertex $v \in V$.  The row corresponding to the hyperedge $e = \{v_1, v_2, \ldots, v_k\} \in E$ represents the constraint between the vertices $ \{v_1, v_2, \ldots, v_k\}$, 
%has $d$ non-zero indeterminate entries %$\mathbf{p}(u)-\mathbf{p}(v)$ (resp.\ $\mathbf{p}(v)-\mathbf{p}(u)$) 
%in the $d$ columns corresponding to each vertex $v_i \in e$ and zero in the other entries.

%generic independence, infinitesimal rigidity
%(based on indeterminates)

%--stress vectors and flex vectors
%(also based on indeterminates)

%--generic isostaticity (minimal rigidity, wellconstrainedness),
%flexibility (not rigid), underconstrained (independent
%and not rigid), overconstrained (dependent -- only briefly
%mentioned
%in this paper; all results are about independent - underconstrained or
%isostatic)

% % % % % % % % % % % % % % % % % % % % % % % % % % % % %

%The problem is equivalent to combinatorially determining the generic rank of the 3-dimensional bar-joint rigidity matrix of a graph.  The $d$-dimensional bar-joint rigidity matrix of a graph $G = (V,E)$, denoted $R_d(G)$, is a matrix of indeterminates. Let $p_1(v), p_2(v), \ldots, p_d(v)$  represent the coordinate position $\mathbf{p}(v) \in \mathbb{R}^d$of the joint corresponding to a vertex $v \in V$.  . The matrix $R_d(G)$ has one row for each edge $e \in E$ and $d$ columns for each vertex $v \in V$.  The row corresponding to $e = \{u,v\} \in E$ represents the bar connecting $p(u)$ and $p(v)$ and has $d$ non-zero indeterminate entries $\mathbf{p}(u)-\mathbf{p}(v)$ (resp.\ $\mathbf{p}(v)-\mathbf{p}(u)$) in the $d$ columns corresponding to $u$ (resp.  $v$) and zero in the other entries.  
%
%A subset of edges $E'$, or a subgraph $(V', E')$, of a graph $G = (V, E)$ is said to be independent (we drop ``bar-joint'' from now on) in $d$-dimensions, when the set of rows of $R_d(G)$ corresponding to $E'$ is generically independent, or independent for a generic instantiation of the indeterminate entries. This yields the $d$-dimensional generic rigidity matroid associated with a graph $G$. The graph is rigid if the number of generically independent rows or the rank of $R_d(G)$ is maximal, i.e., $d|V| - {d+1 \choose 2}$, where ${d+1 \choose 2}$ is the number of rotational and translational degrees-of-freedom of a rigid body in $\mathbb{R}^d$ [?].

\subsection{DR-plan}
%\subsection{Definitions}
%\label{sec:prelim_defs}
%
%% TODO
%
%% A paragraph of preliminaries such as:
%%     - rigidity matrix R,
%%     - stress vectors S one coordinate per edge (w/ SR =E (external stress vector, 2 coordinates  per vertex));
%%     - flex vectors F (2 coordinates per vertex) (right nullspace/kernel of R)
%% Should precede the definition of
%%     + independent,
%%     + overconstrained (not independent),
%%     - rigid (contains an independent set with sufficiently many eedges/constraints)
%%     - isostatic (wellconstrained/minimally rigid), ,
%%     - flexible (not rigid),
%%     + underconstrained (independent and not rigid).
%% After that, define DR plans etc.
%
%In Sections \ref{sec:DRP} and \ref{sec:recomb} a \textbf{graph} is a bar and joint system. $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$. The \textbf{density} of graph $G$ is $d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}$.
%
%Given a constant $k$, a graph $G$ is:
%\begin{itemize}
%    \item \textbf{independent} (or \textbf{sparse}) if, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.
%
%    \item \textbf{over-constrained} if it is not independent.
%
%    \item \textbf{well-constrained} (or \textbf{tight}) if $G$ is independent and $d(G)=k$.
%
%    \item \textbf{rigid} if there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.
%
%    \item \textbf{under-constrained} if $G$ is independent and not rigid.
%
%    % \item \textbf{trivial} if (1) it is over-constrained graph and (2) all of its subgraphs are also trivial. Trivial graphs are input.
%\end{itemize}
%
\textbf{Trivial} graphs are ill-defined in the general case. The only strict requirements are: (1) it must over-constrained and (2) all of its subgraphs are also trivial.

% \begin{definition}
%     A graph is \textbf{over-constrained} if, given constant $k$, there exists some
%     % induced
%     subgraph $S\subseteq G$ such that $d(S) > k$.
% \end{definition}

@@

\begin{definition}\label{def:drp}
    The \textbf{decomposition-recombination \mbox{(DR-)} plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
    \begin{enumerate}
        \item The root of the tree `contains' $G$.
        \item For all nodes, $C$, that `contain' non-trivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item A node with a trivial subgraph is a leaf.
    \end{enumerate}

@@

    An equivalent DAG can be constructed from this tree such that all nodes containing the same subgraphs are combined into one, with all edges preserved.

    Note that nodes will be referred to interchangeably as ``the node that contains the (sub)graph $C$'' and as simply ``$C$''.

    A DR-plan is \textbf{complete} if it satisfies the modified rule number 2: the children are \emph{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. This makes rule 3 implicit. The complete DR-plan is unique.

@@

\subsection{Notation}

In Sections \ref{sec:DRP} and \ref{sec:recomb}, $G$ is taken to be a \emph{well-constrained} bar and joint graph with values $(V,E,w_V,w_E)$.
% \todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.

$Idc(G,X)$ is the graph induced on $G$ with the vertex set $X\subseteq V$. This can also be overloaded such that, using graph $H=(W,F)$, $Idc(G,H)=Idc(G,W)$.

$C$ is the graph in an arbitrary node in $CompleteDRP(G)$. $C_i$ is the $i^{\text{th}}$ child of $C$. By definition of a DR-plan, it is implied that $C_i$ is a well-constrained vertex-maximal proper subgraph.

>>>>

@@

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

%XXXXXXXXXXXXXXX BASICS until combinatorial characterization of 
%independence and rigidity XXXXXXXXXXX

NOTE: geometric constraint systems can have inequalities (the parameters
in $\delta$ being inexact, small intervals of values).

XXXXXXXXXsomething has to be said 
along with asimow roth (infinitesimal rigidity 
implies rigidity)
when the rigidity matrix has appropriate rank
the realizations or solutions of the 
of the corresponding constraint system 
are generically isolated and zero-dimensional 
(if the constraint system has equalities and exact 
values for the parameters $\delta$.
If the constraint system has inequalities, i.e, 
if the $\delta$ lie in an interval,
this claim is approximate: 
the solutions are isolated small, full-dimensional  connected components.

%XXXXXXXX Also in the recombination section, it should be noted
%that the HUGE advantage of the convex Cayley method
%is that it is completely unaffected by having the $\delta$ be intervals
%cite my paper with Heping!!!

%XXXXXXXXXX CUrrently there are open problems strewn throughout the paper. 
%Should they be collected to the conclusion?
%Or at least clearly labeled as open problems?
%XXXXXXXXX

\noindent{\bf Note:}
In the remainder of this section and the next two sections 
\ref{sec:DRP} and \ref{sec:recomb} 
we only consider bar-joint qusecs and graphs
Relevant formal analogies  for the other 2 types of qusecs and (hyper)graphs 
are given in the subsequent 2 sections on Applications.

XXXNow comes the definition of stress vector and flex vector. 
NOTE: something has to be said about what flexes and stresses mean

An {\em external stress} $t$ is a $1\times 2|V|$ vector  (of indeterminates)
which specifies a 2D vector acting at each vertex
such that the stress balance equation $sR = t$ holds, where $s$ is a vector
of internal stresses, one for each bar, and $R$ is the rigidity matrix.

\subsection*{Decomposition-Recombination (DR) Plans}

%$G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$. The \textbf{density} of graph $G$ is $d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}$.

%Given a constant $k$, a graph $G$ is:
%\begin{itemize}
%    \item \textbf{independent} (or \textbf{sparse}) if, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.
%
%    \item \textbf{over-constrained} if it is not independent.
%
%    \item \textbf{well-constrained} (or \textbf{tight}) if $G$ is independent and $d(G)=k$.
%
%    \item \textbf{rigid} if there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.
%
%    \item \textbf{under-constrained} if $G$ is independent and not rigid.
%
%    % \item \textbf{trivial} if (1) it is over-constrained graph and (2) all of its subgraphs are also trivial. Trivial graphs are input.
%\end{itemize}
%
% \begin{definition}
%     A graph is \textbf{over-constrained} if, given constant $k$, there exists some
%     % induced
%     subgraph $S\subseteq G$ such that $d(S) > k$.
% \end{definition}

@@

A \textbf{trivial} graph is   a single vertex.
\begin{definition}\label{def:drp}
    The \textbf{decomposition-recombination \mbox{(DR-)} plan} of graph $G$,
    \cite{XX}
    $DRP(G)$, is defined as a forest that has the following properties:
    \begin{enumerate}
        \item Each  node represents/contains/is  a rigid vertex-induced subgraph of $G$
        %\item For a node, $C$, that is  a non-trivial graph, its $N$
        %    children, $C_1, \ldots, C_N$, are rigid vertex-maximal proper subgraphs of $C$.
        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the 
            vertex set of $C$.
        \item A leaf node is a trivial subgraph.
       \item A root node is a maximal rigid subgraph of $G$
    \end{enumerate}

@@

    An equivalent DAG can be constructed from the above forest such that all nodes
    containing the same subgraphs are identified into a single node.
    In this manuscript, however, we retain a forest as defined above.
    When a graph is isostatic, its DR plan is a tree.

    %Note that nodes will be referred to interchangeably as ``the node that
    %represents or contains the (sub)graph $C$'' and as simply ``$C$''.

    A DR-plan is \textbf{complete} if it satisfies an additional rule: 
        \item For a node, $C$, that is  a non-trivial graph, its $N$
            children, $C_1, \ldots, C_N$, are all of the 
            rigid vertex-maximal proper subgraphs of $C$.
    This makes Rule 2 implicit, and in fact, $C$ contains all the edges in
    the union of its children as well. The complete DR-plan is unique.

@@

%\emph{well-constrained} bar and joint graph with values $(V,E,w_V,w_E)$.
% \todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.

\noindent{\bf Note:}
In Section \ref{sec:DRP} $G$ is assumed to be isostatic.
$Idc(G,X)$ is the subgraph of $G$ induced by the vertex set $X\subseteq V$. 
For a subgraph $H=(W,F)$ of $G$, $Idc(G,H)=Idc(G,W)$.
In general, $C$ is the graph in an arbitrary node in $CompleteDRP(G)$. $C_i$
is the $i^{\text{th}}$ child of $C$. It is implied that 
$C_i$ is an isostatic vertex-maximal proper subgraph.

\subsection*{Importance of an Optimal DR-plan}
The use of a DR-plan in designing especially self-similar qusecs is
immediately clear, as shown in Figures \ref{XX} and \ref{XX}.
In fact, knowing an optimal DR-plan is crucial for design and analysis of 
even non-self-similar qusecs 
and their realizations with various desirable properties.

First, note that the basic task of \underbar{{\sl realizing given qusecs}} would require finding real
 solutions 
 a large multivariate polynomial system (of inequalities and equalities
 representing the constraints). Without DR-planning, this requires double
 exponential time in the number of variables
 (even if orientation type is specified).
With DR-planning, the complexity is dominated by the size of the largest 
subsystem that is
solved, or recombined from the solutions of its child subsystems i.e.,the maximum fan-in occuring in a DR-plan.
Thus finding an optimal DR-plan is important for realization.

Next, using the DR-plan we obtain a \underbar{{\sl recursive block
decomposition of the rigidity matrix}}   
with each block being the rigidity matrix of 
an isostatic subgraph.
The blocks intersect on isostatic or trival subgraphs.
This recursive block decomposition of the rigidity matrix $R$ 
correspondingly \underbar{{\sl recursively decomposes the stress vectors}}
$s$ that balance a given
external stress $t$ since $sR = t$, and moreover, the external stress vector
$t$ now \underbar{{\sl recursively "distributes" as external stresses}} 
for each isostatic subgraph of the DR-plan.
When the rigidity matrix and stress vectors are indeterminates, it can be
used to design  qusecs underlying graph and parameters $\delta$ to obtain an  
optimal distribution of stresses on the geometric primitives. 
When the realization of the qusec is given, this can be used to 
analyze the distribution of a  given external load.

%\subsection{DR-plan}
%%\subsection{Definitions}
%%\label{sec:prelim_defs}
%%
%%% TODO
%%
%%% A paragraph of preliminaries such as:
%%%     - rigidity matrix R,
%%%     - stress vectors S one coordinate per edge (w/ SR =E (external stress vector, 2 coordinates  per vertex));
%%%     - flex vectors F (2 coordinates per vertex) (right nullspace/kernel of R)
%%% Should precede the definition of
%%%     + independent,
%%%     + overconstrained (not independent),
%%%     - rigid (contains an independent set with sufficiently many eedges/constraints)
%%%     - isostatic (wellconstrained/minimally rigid), ,
%%%     - flexible (not rigid),
%%%     + underconstrained (independent and not rigid).
%%% After that, define DR plans etc.
%%
%%In Sections \ref{sec:DRP} and \ref{sec:recomb} a \textbf{graph} is a bar and joint system. $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$. The \textbf{density} of graph $G$ is $d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}$.
%%
%%Given a constant $k$, a graph $G$ is:
%%\begin{itemize}
%%    \item \textbf{independent} (or \textbf{sparse}) if, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.
%%
%%    \item \textbf{over-constrained} if it is not independent.
%%
%%    \item \textbf{well-constrained} (or \textbf{tight}) if $G$ is independent and $d(G)=k$.
%%
%%    \item \textbf{rigid} if there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.
%%
%%    \item \textbf{under-constrained} if $G$ is independent and not rigid.
%%
%%    % \item \textbf{trivial} if (1) it is over-constrained graph and (2) all of its subgraphs are also trivial. Trivial graphs are input.
%%\end{itemize}
%%
%\textbf{Trivial} graphs are ill-defined in the general case. The only strict requirements are: (1) it must over-constrained and (2) all of its subgraphs are also trivial.
%
%% \begin{definition}
%%     A graph is \textbf{over-constrained} if, given constant $k$, there exists some
%%     % induced
%%     subgraph $S\subseteq G$ such that $d(S) > k$.
%% \end{definition}
%
%% \begin{definition}
%%     A graph is \textbf{well-constrained} if, given constant $k$, $d(G) = k$ and for all
%%     % induced
%%     subgraphs $S\subseteq G$, (1) $d(S)\leq k$, or (2) given a set of trivial graphs $T$, $S$ is isomorphic to one of the graphs in $T$ (i.e.\ $S$ is trivial).
%% \end{definition}
%
%
%
%% \begin{definition}
%%     A \textbf{trivial} graph is ill-defined in the general case. The only strict requirements are: (1) it must be an over-constrained graph and (2) all of its subgraphs are also trivial.
%%     \todo{Maybe leave the following out until it's needed later?}
%%     In the familiar geometric cases of $d$-dimensional space, all vertex weights are $d$, all edge weights are $1$, and constant $k= -{{d+1}\choose{2}}$. Trivial graphs for 2D would be a single vertex. Trivial graphs in 3D would be a vertex and an edge (2 vertices with an edge between). Etc. These trivial graphs capture the notion of the rotational symmetry that exists in geometric spaces.
%% \end{definition}
%
%
%\begin{definition}\label{def:drp}
%    The \textbf{decomposition-recombination \mbox{(DR-)} plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
%    \begin{enumerate}
%        \item The root of the tree `contains' $G$.
%        \item For all nodes, $C$, that `contain' non-trivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
%        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item A node with a trivial subgraph is a leaf.
%    \end{enumerate}
%
%    % It can also be described recursively as: the root is $G$, its children are the trivial subgraphs and the DR-plans of its well-constrained vertex-maximal proper subgraphs whose union is $G$ itself.
%
%    An equivalent DAG can be constructed from this tree such that all nodes containing the same subgraphs are combined into one, with all edges preserved.
%
%    Note that nodes will be referred to interchangeably as ``the node that contains the (sub)graph $C$'' and as simply ``$C$''.
%
%    A DR-plan is \textbf{complete} if it satisfies the modified rule number 2: the children are \emph{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. This makes rule 3 implicit. The complete DR-plan is unique.
%
%    A DR-plan is \textbf{optimal} if it minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
%\end{definition}
%
%% \begin{definition}
%%     The \textbf{complete DR-plan} of graph $G$, $CompleteDRP(G)$, is the unique DR-plan but with a modified rule number 2: the children are \emph{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. By this, rule 3 is implicit for a complete DR-plan.
%% \end{definition}
%
%% \begin{definition}
%%     The \textbf{optimal DR-plan} of graph $G$, $OptimalDRP(G)$, is the DR-plan that minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
%% \end{definition}
%
%
%\subsection{Notation}
%
%In Sections \ref{sec:DRP} and \ref{sec:recomb}, $G$ is taken to be a \emph{well-constrained} bar and joint graph with values $(V,E,w_V,w_E)$.
%% \todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
%% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.
%
%$Idc(G,X)$ is the graph induced on $G$ with the vertex set $X\subseteq V$. This can also be overloaded such that, using graph $H=(W,F)$, $Idc(G,H)=Idc(G,W)$.
%
%$C$ is the graph in an arbitrary node in $CompleteDRP(G)$. $C_i$ is the $i^{\text{th}}$ child of $C$. By definition of a DR-plan, it is implied that $C_i$ is a well-constrained vertex-maximal proper subgraph.
